Reply To Examiners

### 2014-04-25 answer_thesis_examiner/chap2.tex
auto

>>>>

\replyToComment
    {Sec 1.1 and 1.2 should be reviewed again ... with proper citations on the background studies.}
    {The sections were reviewed and several citations were added}

\replyToComment
    {Paragraph 1 of Sec 1.3.3 should be removed or rewritten}
    {The paragraph were removed?}

\replyToComment
    {The achievement of objectives should (also) be stated in the conclusion chapter. }
    {These were added into the conclusion chapter (``with proper justfications based on experimental results and findings'').}

\noindent
\begin{longtable}[c]{p{0.14\textwidth}|p{0.12\textwidth}|p{0.34\textwidth}|p{0.24\textwidth}}
\textbf{Page No} & \textbf{Line No} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
 & & & \\
1 & 13 & single SAR channel & single-channel SAR \\ 
 & & & \\
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\[10pt]
ToC & - & missing page numbers & Rectified \\[10pt]
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
ToC & - & missing page numbers & Rectified \\
\end{longtable}

%\noindent
%\begin{tabularx}{\textwidth}{X | X | X X X X}
%  Page No & Line No & \multicolumn{2}{l|}{Comment} & \multicolumn{2}{l}{Reply} \\
%  \hline 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
%          \end{tabularx}
